Package Interconnection

### 2021-09-11 paper/package_interconnection.Rmd
Modify the static network plot.

@@

@@

```{r network-graph, eval = FALSE, fig.cap = "Interaction network between DoE R packages. The color of edges reflect the type of interaction, i.e., depends, imports, and suggests. Nodes' color indicates wether the package is authored by Ulrike Groumping or not."}
# create the graph
ggraph(routes_tidy, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point(aes(color = first_author)) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()
```
Figure \@fig(network-graph) shows the interplay of DoE packages. In the previous section, we noticed that  Ulrike Groemping authored many DoE packages. We also noticed that one of her package, DoE base, is among the most downloaded DoE package on CRAN. Hence, we categorise the package whether it is authored by her or not. The network conveys that there are 5 clusters of interaction with one big cluster.

@@

# Create the categorisation based on main author 
# create the network by facetting by author 
# if there are many authors then create the facet for example if the author write >= 3 packages. 
# not only focus in the Ulrike alone

>>>>

# Interaction

@@

```{r network-graph, fig.cap = "Interaction network between DoE R packages. The color of edges reflect the type of interaction, i.e., depends, imports, and suggests. Nodes' color indicates the authors who wrote more than 2 DoE packages as the first author.", fig.width=12, fig.height = 8}

pkg_nodes_static <- aut_gr %>%
  mutate(first_author = case_when(first_aut == "Ulrike Groemping" ~ "Ulrike Groemping",
                                 first_aut == "John Lawson" ~ "John Lawson",
                                 first_aut == "Robert B. Gramacy" ~ "Robert B. Gramacy",
                                 n <=2 ~ "Other")) %>%
  mutate(first_author = factor(first_author, levels = c("Ulrike Groemping",
                                                        "John Lawson",
                                                        "Robert B. Gramacy",
                                                        "Other"))) %>%
  select(L2, first_author)

# create igraph object
routes_igraph_static <- graph_from_data_frame(d = pkg_edges, vertices = pkg_nodes_static, directed = TRUE)

# create the input based on the igraph object
routes_tidy_static <- routes_igraph_static %>% as_tbl_graph() %>%
  activate(edges)

# create the graph
ggraph(routes_tidy_static, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(3, 'mm')), 
                 end_cap = circle(3, 'mm')) + 
  geom_node_point(aes(color = first_author), size = 4) + 
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  scale_color_manual(values = c("blue", "grey50", "tomato", "magenta")) +
  theme_graph()
```

@@

Figure \@fig(network-graph) shows the interplay of DoE packages. In the previous section, we noticed that  Ulrike Groemping authored many DoE packages. We also noticed that one of her package, DoE base, is among the most downloaded DoE package on CRAN. Hence, we categorise the package whether it is authored by her or not. The network conveys that there are 5 clusters of interaction with one big cluster.

@@
